---
title: "5513 assignment 2"
author: "DIYAO CHEN"
date: "2020/4/24"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Introduction
My research question is What Nintendo future strategies should be? 
For the data wrangling, base on global sales, I chose the top 1000 selling games in the world as my data set.


#loading library
```{r , message = FALSE}
library(tidyverse)
library(readr)
library(kableExtra)
library(ggplot2)
library(lubridate)
library(gridExtra)
library(rmdformats)
library(readxl)
library(reshape2)
```


```{r , message = FALSE, echo=FALSE}
dat<- read_excel("D:\\Rstudioxuexi\\video_games_sales.xlsx")
head(dat)
```

# Future strategy


## In this part, we will analyze historical data to talk about Nintendo's future strange. We will select Nintendo's company all the product in the top1000 hot sell games in the world by the different platform to analysis what is next step with Nintendo.


```{r chunk platform select}
dat4 <- dat %>%
  dplyr::select(Publisher,Platform,Global_Sales) %>%
  dplyr::filter(Publisher == "Nintendo")%>%
 group_by(Platform) %>%
 mutate(Cases = n()) %>%
  unique() %>%
  arrange(Platform)
head(dat4)
```

```{r chunk table}
kable(caption = "All platform in the top1000 hot games sell",dat4)%>%
  kable_styling(bootstrap_options = c("striped","hover"))
```
