---
title: "5513 assignment 2"
author: "DIYAO CHEN"
date: "2020/4/29"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

# Introduction
## My research question is What Nintendo future strategies should be? 
## For the data wrangling, base on global sales, I chose the top 1000 selling games in the world as my data set.



```{r library, message=FALSE,echo=FALSE}
#loading library
library(lubridate)
library(gridExtra)
library(rmdformats)
library(readxl)
library(reshape2)
library(tidyverse)
library(readr)
library(kableExtra)
library(ggplot2)
```


```{r , message = FALSE, echo=FALSE}
# Input data
dat<- read_excel("D:\\Rstudioxuexi\\video_games_sales.xlsx")

```


# histocial data analysis
```{r historical data, echo=FALSE, message=FALSE}
dat2 <- dat %>% dplyr::select(Publisher,Global_Sales)

head(dat2,n=5)

```

```{r analysis Nintendo sell rank ,  message=FALSE, warning=FALSE, echo=FALSE}
dat3<- dat2 %>%
  dplyr::select(Publisher) %>%
  group_by(Publisher) %>%
 mutate(Cases = n()) %>%
  unique() %>%
  arrange(-Cases)


```
# Table
```{r create a table  ,  message=FALSE, warning=FALSE}

kable(caption = "Nintendo's weight of the world's top 1000 best-selling games",dat3)%>%
  kable_styling(bootstrap_options = c("striped","hover"))

```

## Nintendo's percentage in the world's top 1000 best-selling games is 228/1000*100 = 22.8%. 


# Grahp
```{r create a graph  ,  message=FALSE, warning=FALSE}
Graph<- print(dat3)

Graph1<-ggplot()+ geom_point(data=Graph,aes(x=Publisher,y=Cases),fill="red",colour="black")+
  ggtitle("Nintendo's weight of the world's top 1000 best-selling games")
print(Graph1)

```


## As we can see from the graph, Nintendo is a competitive gaming company. The games released by the company are loved by people all over the world. 

# Future strategy

## In this part, we will analyze historical data to talk about Nintendo's future strange. We will select Nintendo's company all the product in the top1000 hot sell games in the world by the different platform to analysis what is next step with Nintendo.

# Table
```{r chunk platform select, message = FALSE, echo=FALSE}
dat4 <- dat %>%
  dplyr::select(Publisher,Platform,Global_Sales) %>%
  dplyr::filter(Publisher == "Nintendo")%>%
 group_by(Platform) %>%
 summarise_at(vars(Global_Sales),
 list(Global_Sales = mean))

```

```{r chunk table, message = FALSE, echo=FALSE}
kable(caption = "Average of all platform in the top1000 hot games sell",dat4)%>%
  kable_styling(bootstrap_options = c("striped","hover"))
```

# Graph
```{r chunk graph, message = FALSE, echo=FALSE}
Graph2<- dat4%>%
  ggplot(aes(x = Platform, y = Global_Sales))+
  geom_bar(stat = "identity")+
  ggtitle("Nintendo's platform performance")+
  theme(axis.text.x=element_text(angle = 90, hjust = 1))
print(Graph2)
```


## As we can see from the graph, the games released by Nintendo, the Wil platform has the best sales. GB and DS platform also performed well.on the other hand, the GC platform has the worst sales. 


# Conclusion
## Talk about the Nintendo company future strategy. Base on the graph*Nintendo's platform performance* and table*Average of all platform in the top1000 hot games sell*. I consider they should Put in more force to develop  Will platform's video games. On the other hand, the Nintendo company should be relatively less invested in the GC platform. The company can also increase the development of GB and DS platforms.
